Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2016-11-18 cbm-rbd-paper.tex
work on sec 5, component prior predictive plot

Let $\Tsysnow$ be the random variable corresponding to $\Rsysnow(t)$,
giving the (random) system failure time for times $t > \tnow$,
conditioned on all information available at $\tnow$,
and $\fsysnow(t)$ be the corresponding density.
Conditional on the realization $\tsysnow$ of $\Tsysnow$, the unit cost rate is 
\begin{align}
g(\tau \mid \Tsysnow = \tsysnow) &=
\begin{cases}
c_p / \tau     & \text{if } \tsysnow \ge \tnow + \tau \\
c_u / \tsysnow & \text{if } \tsysnow  <  \tnow + \tau \,.
\end{cases}
\label{eq:gtau}
\end{align}
Note that here, $\tau$ is a timespan starting from $\tnow$,
and so is a time on a prospective time scale, where $0$ corresponds to $\tnow$.
In contrast, $\tnow$ and $\tsysnow$ are times on an absolute time scale,
where $0$ corresponds to the time of system start-up.
Taking the expectation over $\Tsysnow$ in \eqref{eq:gtau} leads to the expected unit cost rate being
\begin{align}
\gnow(\tau) &= \E[g(\tau \mid \Tsysnow)] = \frac{c_p}{\tau} \Rsysnow(\tau) + c_u \int_0^\tau \frac{1}{t} \fsysnow(\tnow + t) \dd t\,,
\label{eq:gtnowtau}
\end{align}
again incorporating all that is known at time $\tnow$.

@@

Minimizing $\gnow(\tau)$ leads to $\tausnow$,
the optimal moment of maintenance on a prospective time scale.
(Our procedure is illustrated for a number of current times $\tnow$ in Figure~\ref{fig:ghistfig2}.)
The prospective unit cost rate $\cstarnow = \gnow(\tausnow)$ corresponding to $\tausnow$
thus is the lowest unit cost rate attainable for the remaining lifetime of the system,
i.e., for what happens beyond current time $\tnow$.
Also of interest is the total cost rate at $\tnow$, denoted by $\ctotalnow$.
This gives the expected unit cost rate calculated over the full time since system start-up,
under the assumption that maintenance is scheduled for $\tstarnow = \tnow + \tausnow$.
$\ctotalnow$ generally decreases with $\tnow$ since for larger $\tnow$, maintenance costs are spread over a longer time.
However, when many (or few but critical) components fail, $\ctotalnow$ may increase,
since then, system failure becomes much more likely, leading to a higher $\cstarnow$.
For a numerical example, these relations are depicted in Figure~\ref{fig:tauhistfig2}.

@@

%*** not possible / *** to minimize $\gnow(\tau)$ analytically.
***we calculate $\Rsysnow(t)$ on discrete grid from $\tnow$ until some horizon time $\tnow + t_h$.
$t_h$ can be determined by practical considerations,
but generally should reach into the tail of $\Rsysnow(t)$
such that one can be sure to find $\tausnow$.
We calculate $\gnow(\tau)$ on the same grid,
and determine $\tausnow$ as the minimum over this grid.

We approximate the integral in \eqref{eq:gtnowtau} numerically by a sum,
where $\fsysnow(t)$ is calculated via differences of $\Rsysnow(t)$ values on a dense grid.
$\gnow(\tau)$ is likewise evaluated on a dense grid,
and $\tausnow = \arg\min \gnow(\tau)$ is determined as the minimum over the grid.
%The lower index $\tnow$ of the optimal moment of maintenance serves to remind that
%$\tau^*$ depends on $\tnow$, and also on the history of the system.

@@

\begin{figure}
\includegraphics[width=\textwidth]{ghistfig2}
\caption{System reliability and unit cost rate functions for $\tnow = 0,2,4,6,8$
for the system depicted in Figure~\ref{fig:brakesys-layout},
assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$,
and $c_u = 1$, $c_p = 0.2$.}
\label{fig:ghistfig2}
\end{figure}

@@

\begin{table}
\centering
\begin{tabular}{crrrrrrr}
  \toprule
$k$ & $\beta_k$ & $\E[T_i^k]$ & $\ykz$ & $\nkz$ \\
  \midrule
M & $2.5$ & $5$\rule{1.5ex}{0ex} & $75.4$ & $2$\rule{1ex}{0ex} \\
H & $1.2$ & $2$\rule{1.5ex}{0ex} & $ 2.5$ & $1$\rule{1ex}{0ex} \\
C & $2  $ & $8$\rule{1.5ex}{0ex} & $81.5$ & $1$\rule{1ex}{0ex} \\
P & $1.5$ & $3$\rule{1.5ex}{0ex} & $ 6.1$ & $1$\rule{1ex}{0ex} \\
  \bottomrule
\end{tabular}
\caption{Prior parameters for the four component types as used in the numeric examples.}
\label{tab:priorparams}
\end{table}

>>>>

Let $\Tsysnow$ be the random variable corresponding to $\Rsysnow(t)$,
giving the (random) system failure time for times $t > \tnow$,
conditioned on all information available at $\tnow$,
and $\fsysnow(t)$ be the corresponding density.
Conditional on the realization $\tsysnow$ of $\Tsysnow$, the unit cost rate is 
\begin{align}
g(\tau \mid \Tsysnow = \tsysnow) &=
\begin{cases}
c_p / \tau     & \text{if } \tsysnow \ge \tnow + \tau \\
c_u / \tsysnow & \text{if } \tsysnow  <  \tnow + \tau \,.
\end{cases}
\label{eq:gtau}
\end{align}
Note that here, $\tau$ is a timespan starting from $\tnow$,
and so is a time on a prospective time scale, where $0$ corresponds to $\tnow$.
In contrast, $\tnow$ and $\tsysnow$ are times on an absolute time scale,
where $0$ corresponds to the time of system start-up.
Taking the expectation over $\Tsysnow$ in \eqref{eq:gtau} leads to the expected unit cost rate being
\begin{align}
\gnow(\tau) &= \E[g(\tau \mid \Tsysnow)] = \frac{c_p}{\tau} \Rsysnow(\tau) + c_u \int_0^\tau \frac{1}{t} \fsysnow(\tnow + t) \dd t\,,
\label{eq:gtnowtau}
\end{align}
and $\tausnow = \arg\min \gnow(\tau)$.
$\tausnow$, the optimal moment of maintenance as of $\tnow$,
incorporates thus all that is known at current time $\tnow$.
%The lower index $\tnow$ of $\tausnow$ emphasizes that
%depends on $\tnow$, and also on the history of the system.
Figure~\ref{fig:ghistfig2} illustrates this procedure for a number of current times $\tnow$.

@@

Minimizing $\gnow(\tau)$ leads to $\tausnow$,
the optimal moment of maintenance on a prospective time scale.
The prospective unit cost rate $\cstarnow = \gnow(\tausnow)$ corresponding to $\tausnow$
thus is the lowest unit cost rate attainable for the span of the remaining lifetime of the system,
i.e., for what happens beyond current time $\tnow$.
Also of interest is the total cost rate at $\tnow$, denoted by $\ctotalnow$.
This gives the expected unit cost rate calculated over the full time since system start-up,
under the assumption that maintenance is scheduled for $\tstarnow = \tnow + \tausnow$.
$\ctotalnow$ generally decreases with $\tnow$ since for larger $\tnow$, maintenance costs are spread over a longer time.
However, when many (or few but critical) components fail, $\ctotalnow$ may increase,
since then, system failure becomes much more likely, leading to a higher $\cstarnow$.
For a numerical example, these relations are depicted in Figure~\ref{fig:tauhistfig2}.

@@

Since $\Rsysnow(t)$ is not tractable analytically,
we calculate $\Rsysnow(t)$ for values of $t$ on a dense grid spanning from $\tnow$ to some horizon time $\tnow + t_h$.
(The choice of $h_t$ is discussed in more detail below.)
We calculate $\gnow(\tau)$ on the same grid,
and determine $\tausnow$ by minimizing over this grid.
Here, we approximate the integral in \eqref{eq:gtnowtau} numerically by a sum,
where $\fsysnow(t)$ is calculated via differences of $\Rsysnow(t)$ values on the grid.
%$\gnow(\tau)$ is likewise evaluated on a dense grid,
%and $\tausnow = \arg\min \gnow(\tau)$ is determined as the minimum over the grid.

The horizon span $t_h$ can be determined by practical considerations,
but generally should reach far enough into the tail of $\Rsysnow(t)$
such that $\gnow(\tau)$ is not cut off before it reaches its minimum. %one can be sure to find $\tausnow$.
Note that from \eqref{eq:gtnowtau} it is clear that one needs only ****

@@

\begin{figure}
\includegraphics[width=\textwidth]{ghistfig2}
\caption{System reliability and unit cost rate functions for $\tnow = 0,2,4,6,8$
for the system depicted in Figure~\ref{fig:brakesys-layout}
and prior component models as given in Table~\ref{tab:priorparams},
assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$,
and costs $c_u = 1$, $c_p = 0.2$.}
\label{fig:ghistfig2}
\end{figure}

@@

\begin{table}
\centering
\begin{tabular}{crrrrrrr}
  \toprule
$k$ & $\beta_k$ & $\E[T_i^k]$ & $\ykz$ & $\nkz$ \\
  \midrule
M & $2.5$ & $5$\rule{1.5ex}{0ex} & $75.4$ & $2$\rule{1ex}{0ex} \\
H & $1.2$ & $2$\rule{1.5ex}{0ex} & $ 2.5$ & $1$\rule{1ex}{0ex} \\
C & $2  $ & $8$\rule{1.5ex}{0ex} & $81.5$ & $1$\rule{1ex}{0ex} \\
P & $1.5$ & $3$\rule{1.5ex}{0ex} & $ 6.1$ & $1$\rule{1ex}{0ex} \\
  \bottomrule
\end{tabular}
\caption{Prior parameters for the four component types as used in subsequent numerical examples.
The corresponding expected failure behaviour is visualized in Figure~\ref{fig:comppriorfig1}.}
\label{tab:priorparams}
\end{table}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{comppriorfig1}
\caption{Prior predictive reliability functions corresponding to the values from Table~\ref{tab:priorparams},
%for the four component types of the system depicted in Figure~\ref{fig:brakesys-layout},
showing the expected failure behaviour according to this choice of parameters.}
\label{fig:comppriorfig1}
\end{figure}
